\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-22 notes/2loopNLSM.tex
some final edits

It is instructive to see how both of the constructions in \cref{eq:TwoNLSMMethods} produce valid tree-level amplitudes for the pion. First we will start with $Y$ particles on legs 1 and 4. Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
\begin{align}
n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
\\
 n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})\, .
\end{align}
Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result,
\be\label{eq:NLSMYZ4point}
A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}\, .
\end{equation}
For the $Z$ and $\bar{Z}$ configuration, the numerators are 
\begin{align}
n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
\\
 n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}\, ,
\end{align}
where we have used the shorthand
\begin{equation}
{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}\, .
\end{equation}
The polarization vector of the $\bar{Z}$ particle has not been contracted into the numerators above, resulting in the free $\mu_1$ index.
These numerators produce the partial amplitude
\begin{equation}
A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}\, .
\end{equation}
Plugging in the on-shell polarization of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}. Indeed, this construction is valid to all multiplicity at tree-level. One can see this by considering the only two possible factorization channels that contribute to each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut,
\begin{align} \label{YZCut1}
A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
\\
&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...) \, . \label{YZCut2}
\end{align}
Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states. As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell \jm{I'm confused again.}, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes. Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell. This is essentially what $J$-theory does, as we will show below.

>>>>

It is instructive to see how both of the constructions in \cref{eq:TwoNLSMMethods} produce valid tree-level amplitudes for the pion. First we will start with $Y$ particles on legs 1 and 4. Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
\begin{align}
n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
\\
 n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})\, .
\end{align}
Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result,
\be\label{eq:NLSMYZ4point}
A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}\, .
\end{equation}
For the $Z$ and $\bar{Z}$ configuration, the numerators are 
\begin{align}
n^{\bar{Z}Z}_s &= {}_4\langle F^{3}F^{2}\rangle_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
\\
 n^{\bar{Z}Z}_t &=   {}_2\langle F^{3}F^{4}\rangle_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}\, ,
\end{align}
where we have used the shorthand
\begin{equation}
{}_x \langle F^{a_1}F^{a_2}\cdots F^{a_n}\rangle _{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}\, .
\end{equation}
The polarization vector of the $\bar{Z}$ particle has not been contracted into the numerators above, resulting in the free $\mu_1$ index.
These numerators produce the partial amplitude
\begin{equation}
A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}\, .
\end{equation}
Plugging in the on-shell polarization of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}. Indeed, this construction is valid to all multiplicity at tree-level. One can see this by considering the only two possible factorization channels that contribute to each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut,
\begin{align} \label{YZCut1}
A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
\\
&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...) \, . \label{YZCut2}
\end{align}
Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states. As long as we plug in valid on-shell states for $Z$ and $\bar{Z}$ from \cref{eq:onShellZStates}, these numerators will produce NLSM ordered amplitudes. Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constructions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell. This is essentially what $J$-theory does, as we will show below.
